%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
\vspace{-0.3cm}

  \cventry
    {Senior Software Engineer} % Job title
    {\href{https://uplight.com/}{Uplight}} % Organization
    {Vancouver, BC, Canada} % Location
    {October 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Led technical work on energy analytics products, using \textbf{Databricks and Spark} to derive insights from large datasets.}
        \item{Functioned as a key capacity engine, individually closing a third of team story points and increasing team velocity by 50\% through hands-on \textbf{pairing and mentorship} of junior engineers.}
        \item{Reduced PagerDuty alerts by 90\% by leading a working group to standardize incident management.}
        \item{Drove critical cloud migration efforts, successfully transitioning infrastructure and services for key projects from AWS to GCP.}
      \end{cvitems}
    }

  \cventry
    {Technical Lead} % Job title
    {\href{https://www.thrive.health}{Thrive Health}} % Organization
    {Vancouver, BC, Canada} % Location
    {December 2017 - October 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Led and mentored \textbf{6 direct reports}, responsible for foundational infrastructure and strategic technical direction.}
        \item{Scaled critical APIs for the Canada COVID-19 app to support \textbf{millions of users}.}
        \item{Architected \textbf{access control lists}, ensuring robust privacy and preventing data breaches for sensitive health data.}
        \item{Developed a scalable event tracking system that maintained data residency in Canada and provided vital insights to public health officials.}
        \item{Improved team processes by facilitating retrospectives and 5 Whys sessions, fostering continuous improvement.}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Technical Lead} % Job title
    {\href{https://www.clir.eco}{Clir Renewables}} % Organization
    {Richmond, BC, Canada} % Location
    {April 2017 - November 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Led a team of 3 software developers in building a wind farm analysis tool (\textbf{Python} backend, \textbf{React} frontend).}
        \item{Established core infrastructure, including a build server, user tracking, and secure secret management.}
        \item{Optimized \textbf{AWS} deployment by restructuring security groups, IAM roles, and VPC subnets.}
        \item{Migrated time-series data from Elasticsearch to Redshift, significantly improving data reliability and query speed.}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Principal Software Engineer} % Job title
    {\href{http://pulseenergy.com}{Pulse Energy} (Acquired by EnerNOC then \href{https://www.yardi.com}{Yardi})} % Organization
    {Vancouver, BC, Canada} % Location
    {September 2008 - April 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Designed and built a time-series database in Java using \textbf{Cassandra}, managing terabytes of smart meter data.}
        \item{\textbf{Patented an algorithm} for forecasting energy consumption based on historical conditions and weather data.}
        \item{Automated cloud infrastructure provisioning in EC2 using Chef recipes.}
        \item{Established a comprehensive monitoring stack (Logstash, Kibana, Graphite, Statsd, custom Graphiti-fork).}
        \item{Managed technical recruiting processes, including designing and evaluating coding challenges.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {\href{http://businessobjects.com}{Business Objects} (Acquired by \href{https://www.sap.com}{SAP})} % Organization
    {Vancouver, BC, Canada} % Location
    {July 2006 - September 2008 } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Developed server-side components in C++ and Java.}
        \item{Feature owner of licensing technology and Java container server.}
      \end{cvitems}
    }

\end{cventries}
